Global optimization method with dual Lipschitz constant estimates for problems with non-convex constraints\thanks{This research was supported by the Russian Science Foundation, project No. 16-11-10150.}

### 2020-03-31 2019/NUMTA_Barkalov/SoftComputing/article.tex
Fix second questions of reviewer

	This statement can be interpreted as the incomparability of the local and global characteristics: the global characteristic of the best interval is always larger. At the same time, it follows from the formulae (\ref{R_glob_1}), (\ref{R_glob_greater_R_loc}) that 
\begin{equation}\label{R_glob_equal_R_loc}
	R_{glob}(i) = \rho R_{loc}(i),
\end{equation}
where $\rho=\Big(\frac{1-1/r_{M}^{glob}}{1-1/r_{M}^{loc}}\Big)^2$, if $\nu(x_{i-1})=\nu(x_i)=M$, and $\rho=1$, if $\nu(x_{i-1}) \neq \nu(x_i)$. In the case of the multiplication by the coefficient $\rho$, the local and global characteristics of the search intervals become comparable, and one can choose the best (i.e. the largest) one.

	Based on the relation (\ref{R_glob_equal_R_loc}), one can formulate an \textit{index algorithm with dual estimate of the Lipschitz constants} (hereafter referred to as IA-DL).

@@

	Let us formulate and prove the convergence conditions for the new algorithm IA-DL.\\
	{ \color{red}

@@

@@

	At every iteration of the IA-DL method there will exist such interval $[x_{j-1}, x_j]$, $j=j(k)$, that $\bar x \in [x_{j-1}, x_j]$. According to our assumption that $\bar y = y(\bar x)$ is not the limit point, there will exist such number $\bar k$, starting from which the trial points will not fall into the interval $[x_{j-1}, x_j]$. That is, to conduct a new trial at the point $x^{k+1} \in [x_{t-1}, x_t]$ for each $k\geq \bar k$ such interval $[x_{t-1}, x_t], t=t(k)$ will be selected that $t(k) \neq j(k)$.

@@

	Therefore, for large enough $k$, the following inequality will be true
\begin{equation}
	R_{glob}(j) > \rho R_{loc}(t).
\end{equation}
{\color{red}

Indeed, both $j$ and $t$ depend from $k$, as the numbering of the trial points (by the lower index) changes at every iteration and the numbering of the intervals changes respectively.
%new text begin
However, $R_{glob}(j(k))>0$ is fixed for each $k \geq \bar k$ because $j(k)$ corresponds to the same interval for $k \geq \bar k$, whereas number $t(k)$ corresponds to different intervals with different characteristics $R_{loc}(t(k)) \rightarrow 0$. From this we can conclude that the condition $R_{glob}(j) > \rho R_{loc}(t)$ is fulfilled for a large enough value of $k$.
%new text end
}

Hence, according to Rules 5 and 6 of the IA-DL method the next iteration falls into the interval $[x_{j-1}, x_j]$, which contradicts our assumption regarding the non-limit nature of the point $\bar x$. The theorem is proven.

>>>>

{ \color{blue}

	This statement can be interpreted as the incomparability of the local and global characteristics: the global characteristic of the best interval is larger if $\nu(x_{i-1})=\nu(x_i)=M$. At the same time, it follows from the formula (\ref{R_glob_greater_R_loc}) that

\begin{equation}\label{R_glob_equal_R_loc}
	R_{glob}(i) = \left( \frac{1-\frac{\mu}{\mu_M r_M^{glob}}}{1-\frac{\mu}{\mu_M r_M^{loc}}} \right)^2 R_{loc}(i),
\end{equation}
wherein the maximum value of the equalization coefficient is 
\begin{equation}\label{new_rho}
\rho=\left(\frac{1-1/r_{M}^{glob}}{1-1/r_{M}^{loc}}\right)^2 
\end{equation}
in the case when $\mu = \mu_M$. %, where $\mu = |z_i-z_{i-1}|/\Delta_i$ and $\mu_M$ is from (\ref{current_lower_bounds}).
The use of the equalization coefficient equal to $\rho$ from (\ref{new_rho}) in all cases will correspond to equalizing the largest possible difference between the values of $R_{loc}(i)$ and $R_{glob}(i)$ and will contribute to a more local nature of the search when the difference between $R_{loc}(i)$ and $R_{glob}(i)$ is not the largest, i.e. when $\mu < \mu_M$.

%Использование нормирующего коэффициента равного $\rho$ из (\ref{new_rho})  будет соответствовать выравниванию наибольшей возможной разницы между значениями $R_{loc}(i)$ и $R_{glob}(i)$ и будет способствовать более ``локальному'' характеру поиска в случае когда разница между $R_{loc}(i)$ и $R_{glob}(i)$ не является максимальной (т.е. когда $\mu_M > \mu$).

Based on the relations (\ref{R_glob_equal_R_loc}) and (\ref{new_rho}), one can formulate an \textit{index algorithm with dual estimate of the Lipschitz constants} (hereafter referred to as IA-DL).

@@

	Let us formulate and prove the convergence conditions for the new algorithm IA-DL.\\
	{ \color{blue}

@@

The lemma is proved.
}

@@

	At every iteration of the IA-DL method there will exist such interval $[x_{j-1}, x_j]$, $j=j(k)$, that $\bar x \in [x_{j-1}, x_j]$. 
	{ \color{blue}
	According to our assumption that $\bar y = y(\bar x)$ is not the limit point, there will exist such number $\bar k$, starting from which the trial points will not fall into the interval $[x_{j-1}, x_j]$. That is, to conduct a new trial at the point $x^{k+1} \in [x_{t-1}, x_t]$ for each $k\geq \bar k$ such interval $[x_{t-1}, x_t], t=t(k),$ will be selected that $t(k) \neq j(k)$.
	}

@@

	Therefore, for large enough $k$, the following inequality will be true
\begin{equation}
	R_{glob}(j) > \rho R_{loc}(t).
\end{equation}
{\color{blue}
Indeed, both $j$ and $t$ depend from $k$, as the numbering of the trial points (by the lower index) changes at every iteration and the numbering of the intervals changes respectively.
%new text begin
However, $R_{glob}(j(k))>0$ is fixed for each $k \geq \bar k$ because $j(k)$ corresponds to the same interval for $k \geq \bar k$, whereas number $t(k)$ corresponds to different intervals with different characteristics $R_{loc}(t(k)) \rightarrow 0$. From this we can conclude that the condition $R_{glob}(j) > \rho R_{loc}(t)$ is fulfilled for a large enough value of $k$.
%new text end
}

Hence, according to Steps 5 and 6 of the IA-DL method the next iteration falls into the interval $[x_{j-1}, x_j]$, which contradicts our assumption regarding the non-limit nature of the point $\bar x$. The theorem is proven.
